%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Kakao} % Organization
    {Pangyo, S.Korea} % Location
    {Sep. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing a Messenger application(KakaoTalk) for Windows Desktop using C++, SQLite.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Software Engineer} % Job title
    {Ascan(Start-up)} % Organization
    {Seoul, S.Korea} % Location
    {May. 2015 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Chromium based Desktop WebApp including Shell
    Extensions using CEF, Boost, AngularJS for file sharing \& version management.}
        \item {Wrote Python and Batch scripts automate the full build, packging and deployment cycle running on Jenkins.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Kakao} % Organization
    {Pangyo, S.Korea} % Location
    {Feb. 2014 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Joined to the KakaoTalk messenger for Windows Desktop product team and developed various features such as Accessibiilty support, UI, updater and security enhancement. }
        \item {Developed backends with ASP.NET/Flask \& mongodb stack for internal use.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Support Engineer} % Job title
    {Microsoft} % Organization
    {Seoul, S.Korea} % Location
    {May. 2011 - Jan. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {WDK/SDK Developer Support. Provided development consulting \& advisory services for customers with troubleshooting and extensive debugging.}
        \item {OEM/Embedded Products Support. Also helped customers to build their software and hardware for Windows Embedded products including Windows Mobile, Windows CE, PosReady, and etc.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {DevGuru} % Organization
    {Seoul, S.Korea} % Location
    {Nov. 2009 - Mar. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a QMI linux network device driver and its user library for Verizon Pantech UML290 4G LTE USB Modem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {AhnLab} % Organization
    {S.Korea} % Location
    {Sep. 2003 - Feb. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a Filter Device Driver and User Modules which provides real-time monitoring via kernel/user hooking (API \& SDT) for an Anti-online game hacking product to protect system from illegal behaviors.}
        \item {Researched hacking issues, debugging and Windows internals to design and implement products.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Security Wizard} % Organization
    {S.Korea} % Location
    {Feb. 2001 - Jun. 2003} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a personal firewall engine for driver control and firewall rule management including LSP filtering module, NDIS TDI Device Driver for Win9X, and NT.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
